High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-30 notebooks/mnist.qmd

bmk = benchmark(
    counterfactual_data; 
    models=model_dict, 
    generators=generator_dict, 
    measure=measures,
    suppress_training=true, dataname="MNIST",
    n_individuals=5,
    factual=0, target=1,
    initialization=:identity,
)

Serialization.serialize(joinpath(output_path, "mnist_benchmark.jls"), bmk)
```

>>>>

bmk = benchmark(
    counterfactual_data; 
    models=model_dict, 
    generators=generator_dict, 
    measure=measures,
    suppress_training=true, dataname="MNIST",
    n_individuals=5,
    factual=0, target=1,
    initialization=:identity,
)
CSV.write(joinpath(output_path, "mnist_benchmark.csv"), bmk())
```
